---
title: "Homework 7"
author: ' '
date: ""
output:
  html_document: default
  pdf_document: default
---

(3 points) Read the file Mystery shopping. the description of the file is provided in the separate file.
Run some summary statistics and make visualizations to identify variables which can be used for cluster analysis in order to categorize the employees of the company.Make sure to the variables selected by you are numeric.

```{r}
data <- read.csv("Mystery shopping.csv")

```


(7 points) Check if the measurement scale for each selected variable is similar or do we need normalization? If we need, scale the variables before clustering task.
Run hierarchical cluster analytsis on the variables identified in the previous question.
Plot a dandrogram and comment on how many clusters it is effective to choose after choosing the number of clusters to be chosen, save teh cluster membership variable. 

```{r}


```


(7 points)_Use the kmeans algorithm to build the clusters to categorize employees based on the variables of your choice.
Run the analysis using several number of clusters (k) 
Comment on which model is better? Save the cluster memberships of the best model 

```{r}

```
(5 points)Aggregate the average data for all the variables by clusters
 that you chose in the previous questions. What are the differences 
between those clusters? Try to give a general description of them.
```{r}


```

(8 points)Make 4-5 visualizations based on the the newly created cluster membership variables both from the one generated by the hierarchical method and kmeans method.
Also use the variables which were not included in the model to comment on what kind of employees are gathered in each cluster. 
```{r}

```
