---
title: "Homework 1"
author: "Kevork Sulahian"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=F, message=F)
```


## Read the dataset movies3.csv into R 

```{r}
movies = read.csv("movies3.csv")
```

## The variable gross_adjusted is showing gross box office of the movie adjusted by inflation. The variable budget_adjusted shows the budget of the movie adjusted by inflation

Write a code that will make variables gross_adjusted and budget_adjusted in 1000 USD.
Dont create new variable, just overwrite the old ones. (1 point)

```{r}
gross <- paste0(movies$gross_adjusted, " USD")
budget <-paste0(movies$budget_adjusted, " USD")
```


What is the minimum for box office ?
What is the minimum for budget ? (1 point)

```{r}
movies[movies$gross ==min(movies$gross),]
movies[movies$budget == min(movies$budget),]
```

The variable genre_first is showing which genre was mentioned first on the movies imdb webpage

How many Action movies are there?
How many comedies ? (2 point)

```{r}
tb <- table(movies$genre_first)

# 721 Action
# 844 Comedy
```


Create a new dataframe with the most popular geners. Take those movies only, whose genre appear in the dataframe more than 100 times.(3 points)

Hint
Suppose you want to subset the mtcars dataset in a way that will have only cars who has 6 or 8 cylinder. One way to go with it is the following:
df <- mtcars[mtcars$cyl == 6 | mtcars$cyl ==8,]

However the most efficient way will be:
df <- mtcars[mtcars$cyl %in% c(6,8),]


```{r}
library(dplyr)
tb_names <- names(tb[tb >100])
top_movies <- filter(movies, genre_first %in% tb_names)
head(top_movies)
```

what is the standard deviation of the imdbRating.(2 points)
Hint. If you are getting NA after running the function, one reason can be that the variable has NA inside. Look at the help of the function, specifically for the argument na.rm 

```{r}
sd(movies$imdbRating, na.rm = TRUE)
```

On average, which gener has made the highest box office revenue ? (5 points)

Hint: use function ?aggregate (https://goo.gl/DUyftz) or anything else, but dont give me lenghty code

```{r}
a <-aggregate(top_movies, by = list(top_movies$genre_first), FUN = 'mean', drop = TRUE, simplify = TRUE)
a <- a[c("Group.1","gross_adjusted")]
a
```

Using ggplot construct scatterplot between imdbRating and Metascore. (3 points)


```{r}
library(ggplot2)
attach(top_movies)
ggplot(top_movies, aes(x = imdbRating, y = Metascore)) + geom_point() + ggtitle("scatterplot between imdbRating and Metascore")
  
```

Do the same thing for each genre (using facet_grid() or facet_wrap()) (3 points)

```{r}
ggplot(top_movies, aes(x = imdbRating, y = Metascore)) + geom_point() + ggtitle("scatterplot between imdbRating and Metascore") + facet_grid(.~genre_first)

```

Construct histogram for imdbRating for each genre (3 point)

```{r}
ggplot(top_movies, aes(x = genre_first, y = imdbRating, fill = genre_first)) + geom_histogram(stat = "identity") +
  ggtitle("Histogram for IMDB rating for each genre")
```

Calculate mean, median and standard deviation of imdbRating and Metascore for each genre.(4 points)

```{r}
mean(imdbRating, na.rm = T)
median(imdbRating, na.rm = T)
sd(imdbRating, na.rm = T)

mean(Metascore, na.rm = T)
median(Metascore, na.rm = T)
sd(Metascore, na.rm = T)
```

Based on the previous 3 questions, describe your findings in one paragraph.(5 poits)

### the Mean and Median is higher in IMDB while Standard Deviation

Create a binary variable based on the column OscarWon taking the valu 1, if the film got an Oscar and 0 if it does not. You can use ifelse for this.(3 points)
```{r}
top_movies$binary_var = ifelse(OscarWon > 0, 1, 0)
```

Write a code to see what genre films have the highest probability of being awarded Oscar(2 points)
```{r}
a <- top_movies %>% group_by(genre_first) %>% summarise(won = sum(binary_var))
a[order(-a$won),] 

```

use visualization to illustrate the difference in means of budgets of films winning Oscar with those not winning one.(3 points)

```{r}
a <- top_movies %>% group_by(binary_var) %>% summarise(means = mean(gross_adjusted))
ggplot(a, aes(x = a$binary_var,y = a$means, fill = a$binary_var)) + geom_histogram(stat= "identity") +
  labs(x = "No Oscar vs at least 1 Oscar", y = "Budget", title = "Budget on oscar winning movies")
```